|

### 2020-03-19 paper/paper.Rmd
after knitting and sending that copy to ben d and just before doing a reorganization to try to keep this repo wieldy
getting there

title: |
    New and old ways to chase a rabbit:  
    Differential item functioning detection methods
subtitle: |
    Ben Stenhaug  
    Stanford University
abstract: |
  summarize propose extensions insist as dif as student property and on communicating uncertainty
  <!-- https://tinyurl.com/ybremelq -->
header-includes: 
- \usepackage{amsmath}
- \DeclareMathOperator*{\argmax}{arg\,max} # for gini coefficient
- \DeclareMathOperator*{\argmin}{arg\,min} # for gini coefficient

@@

# DIF methods

@@

# Next steps

```{r child = "paper_3_next_steps.Rmd"}
```

>>>>

title: |
    Promise and peril: Agnostic identification methods  
    for detecting differential item functioning
subtitle: |
    Ben Stenhaug, Ben Domingue, and Mike Frank  
    Stanford University
abstract: |
  It is well known that likelihood ratio tests (LRT) are effective at detecting differential item functioning (DIF) in item response models. However, to use an LRT, a model identifying assumption needs to be made so that differences in group ability can be disentangled from potential DIF. We use the term "agnostic identification" (AI) to describe the process of finding such identifying assumptions without a priori knowledge of relative group ability or items that are DIF-free. We summarize existing AI methods and propose a variety of new methods. We conduct a simulation study — which we argue is more realistic than most DIF simulation studies in the literature — and find that one of the proposed new AI methods, All-others-as-anchors-one-at-a-time (AOAA-OAT), significantly outperforms current methods. We also offer a new method, the equal means, multiple imputation logit graph (EM-MILG), that clearly presents all information about possible DIF, including sampling variability in item parameters, to the analyst. \clearpage <!-- https://tinyurl.com/ybremelq -->

header-includes: 
- \usepackage{amsmath}
- \DeclareMathOperator*{\argmax}{arg\,max} # for gini coefficient
- \DeclareMathOperator*{\argmin}{arg\,min} # for gini coefficient

@@

# Agnostic identification methods

@@

# Simulation study {#simstudy}

```{r child = "paper_3_sim.Rmd"}
```
